Modeling Interventions

### 2021-03-09 paper/paper.Rmd
tweaks

---
title             : "Towards a ``Standard Model'' of Early Language Learning"
shorttitle        : "Standard Model of Language Learning"

@@

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

>>>>

---
title             : "Towards a \"Standard Model\" of Early Language Learning"
shorttitle        : "Standard Model of Language Learning"

@@

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
